Incentivizing Exploration by Heterogeneous Users

### 2018-02-16 algorithm.tex

The algorithm achieving the claimed bounds of
Theorem~\ref{thm:main-overview} is fairly simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled, 
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way the algorithm ensures that each arm is pulled often enough.

@@

Our main result is that Algorithm~\ref{alg:basic-incentivizing} achieves $O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3)$ cumulative regret with $O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right)$ payment budget.  This is stated in the following pair of theorems.

\dkcomment{Depending on how we structure Section 3, we might
get rid of those theorems, and only consider them parts of Theorem 2
that we prove here.}

\begin{theorem}
The expected payment budget for
Algorithm~\ref{alg:basic-incentivizing} is bounded above by
\begin{align}
O \left(\ARMNUM^2 \MAXR \Diam^2 \TieDensity d^3 \sigma\cdot \exp(\frac{2}{\MinProb}) \right). \nonumber 
\end{align} 
\label{rst:budget}
\end{theorem}

\begin{theorem}
For any given $T$, the expected cumulative regret for
Algorithm~\ref{alg:basic-incentivizing} up to time $T$ is bounded
above by 
\begin{align}
O \left(\MAXR\cdot  N\exp(\frac{2}{p})\right) +
O(\ARMNUM\Diam^2 d^2\sigma^2 \TieDensity(\log(T))^3).
\end{align}
\label{rst:regret}
\end{theorem}

\dkcomment{I had written ``exponentially'' in a few places here, but I
  don't think that was correct. The error only decreases as
  $\sqrt{s}$, while the probability of deviating beyond that error
  decreases exponentially.}
The high-level idea of the proof of Theorem~\ref{thm:main-overview}
is the following.
Because the algorithm ensures that each arm is pulled
``frequently enough,''
the estimates \ArmEV{t}{i} become gradually more accurate in the
phase number $s$.
Thus, the fraction of agents who misidentify their best arm decreases.
Because for each arm, enough agents have a true preference for this
arm, once the arms' attribute vectors are learned well enough,
the algorithm will not need to incentivize any more,
resulting in a payment bound independent of $T$.
Similarly, the regret will decrease, and mostly accrue
due to ``problematic'' agents who are nearly tied in their preferences
between their top two arm choices.
The detailed analysis following this outline is somewhat subtle, though,
due to the dependencies between the agents' arm pulls and the
estimates which in turn are based on past arm pulls.
We begin with several technical lemmas that are used for both the
payment and regret bounds.

@@

>>>>

The algorithm achieving the claimed bounds of
Theorems~\ref{rst:budget} and~\ref{rst:regret} is fairly simple.
It mostly allows agents to exploit, but when an arm is sufficiently
unlikely to be pulled, 
the algorithm incentivizes this arm with a payment high enough
to guarantee that the next agent pulls it.
This way the algorithm ensures that each arm is pulled often enough.

@@

The high-level idea in the proofs of our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret},
is the following.
Because the algorithm ensures that each arm is pulled
``frequently enough,''
the estimates \ArmEV{t}{i} become gradually more accurate in the
phase number $s$.
Thus, the fraction of agents who misidentify their best arm decreases.
Because for each arm, enough agents have a true preference for this
arm, once the arms' attribute vectors are learned well enough,
the algorithm will not need to incentivize any more,
resulting in a payment bound independent of $T$.
Similarly, the regret will decrease, and mostly accrue
due to ``problematic'' agents who are nearly tied in their preferences
between their top two arm choices.
The detailed analysis following this outline is somewhat subtle, though,
due to the dependencies between the agents' arm pulls and the
estimates which in turn are based on past arm pulls.
We begin with several technical lemmas that are used for both the
payment and regret bounds.

@@

We now prove our main results, Theorems~\ref{rst:budget} and~\ref{rst:regret}.
